### 2012-01-23 GUIErrorDetector/paper/introduction.tex
add refs and fix the typos

%It may work during development, but like most concurrent bugs, you'll start to see weird exceptions come up that seem completely unrelated, and occur non-deterministly - usually spotted AFTER you've shipped by real users. Not good.

@@

   org.mozilla.gecko.gfx.LayerView.<init>(Context;LayerController)
-> android.opengl.GLSurfaceView.setRenderer(GLSurfaceView\$Renderer;)
-> java.lang.Thread.start()
-> android.opengl.GLSurfaceView\$GLThread.run()
-> android.opengl.GLSurfaceView\$GLThread.guardedRun()
-> org.mozilla.gecko.gfx.LayerRenderer.onSurfaceChanged(GL10;II)
-> org.mozilla.gecko.gfx.LayerView.setViewportSize(IntSize;)
...
-> android.view.ViewRoot.checkThread()
\end{alltt}
\end{CodeOut}
\vspace*{-2.0ex} \Caption{{\label{fig:report} A report
generated by our tool to reveal the pontential error in
Figure~\ref{fig:androiderror}. This report indicates a 
full method call chain that causes the error. $\rightarrow$ represents
the call relationship
between methods, and \CodeIn{checkThread} is an Android library
method  that checks whether the current thread is the
event dispatching thread before accessing a GUI object.
}} %\vspace{-5mm}
\end{figure}

@@

We instantiated our technique for four popular GUI frameworks namely SWT,
eclipse plugin environment, Java Swing, and Android. 
Swing and SWT are unquestionably 
two dominating GUI frameworks in developing desktop Java applications.
Eclipse and its plugin development envrionment is the de-facto standard
IDE for Java. Android is the No. 1 platform for
developing mobile applications with market share 56\% as of Sep 2011.
Although our technique is generally applicable for GUI
frameworks adapting the single-thread rule, a specific framework
may have its own treatment of \textit{UI thread} and \textit{call graph
entry nodes}. Thus, we must explicitly identify those framework-specific
parts in our prototype tool implementation.

@@

We implement an invalid thread error detection tool that supports
the above four GUI frameworks. Our tool works in a fully-automatic,
push-button manner, and scales to realistic programs.
We evaluate our implementation on XXX subjects from four different
frameworks over XXX LOC. The experiment results demonstrate
that: our technique is effective (it found XXX real-world errors
on all supported frameworks, and produced significantly less
false positives and redundant warnings than the simple analysis);
our reflection-aware call graph construction algorithm is
critical in finding errors in Android applications,
%graph construction algorithm is useful (XXX it improves both completeness
%and precision over the existing algorithms), 
and our proposed
heuristics are useful (it signficantly reduces the number of
false positives and redundant warnings).

@@

\item \textbf{Evaluation.} We performed an experiment on XXX subjects
from 4 different platforms over XXX LOC to show the usefulness
of the proposed techinque (Section~\ref{sec:evaluation}).

>>>>

%It may work during development, but like most concurrent bugs, you'll start to see weird exceptions come up that seem completely unrelated, and occur non-- usually spotted AFTER you've shipped by real users. Not good.

@@

   org.mozilla.gecko.gfx.LayerView.<init>(Context;LayerController)
-> android.opengl.GLSurfaceView.setRenderer(GLSurfaceView\$Renderer;)
-> java.lang.Thread.start()
-> android.opengl.GLSurfaceView\$GLThread.run()
-> android.opengl.GLSurfaceView\$GLThread.guardedRun()
-> org.mozilla.gecko.gfx.LayerRenderer.onSurfaceChanged(GL10;II)
-> org.mozilla.gecko.gfx.LayerView.setViewportSize(IntSize;)
...
-> android.view.ViewRoot.checkThread()
\end{alltt}
\end{CodeOut}
\vspace*{-2.0ex} \Caption{{\label{fig:report} A report
generated by our tool to reveal the potential error in
Figure~\ref{fig:androiderror}. This report indicates a 
full method call chain that causes the error. $\rightarrow$ represents
the call relationship
between methods, and \CodeIn{checkThread} is an Android library
method  that checks whether the current thread is the
event dispatching thread before accessing a GUI object.
}} %\vspace{-5mm}
\end{figure}

@@

We instantiated our technique for four popular GUI frameworks namely SWT,
eclipse plugin environment, Java Swing, and Android. 
Swing and SWT are unquestionably 
two dominating GUI frameworks in developing desktop Java applications.
Eclipse and its plugin development environment is the de-facto standard
IDE for Java. Android is the No. 1 platform for
developing mobile applications with market share 56\% as of Sep 2011.
Although our technique is generally applicable for GUI
frameworks adapting the single-thread rule, a specific framework
may have its own treatment of \textit{UI thread} and \textit{call graph
entry nodes}. Thus, we must explicitly identify those framework-specific
parts in our prototype tool implementation.

@@

We implement an invalid thread error detection tool that supports
the above four GUI frameworks. Our tool works in a fully-automatic,
push-button manner, and scales to realistic programs.
We evaluate our implementation on XXX subjects from four different
frameworks over XXX LOC. The experiment results demonstrate
that: our technique is effective (it found XXX real-world errors
on all supported frameworks, and produced significantly less
false positives and redundant warnings than the simple analysis);
our reflection-aware call graph construction algorithm is
critical in finding errors in Android applications,
%graph construction algorithm is useful (XXX it improves both completeness
%and precision over the existing algorithms), 
and our proposed
heuristics are useful (it significantly reduces the number of
false positives and redundant warnings).

@@

\item \textbf{Evaluation.} We performed an experiment on XXX subjects
from 4 different platforms over XXX LOC to show the usefulness
of the proposed technique (Section~\ref{sec:evaluation}).

### 2012-01-23 GUIErrorDetector/paper/technique.tex
add refs and fix the typos

Our algorithm in Figure~\ref{fig:detectalgorithm} works as follows. It
first constructs a static call graph for the tested program (line 2),
then specifies entry nodes for it (line 3). The algorithm starts to traverse
the call graph from every entry node (line 6). For every entry node,
it first uses Breadth First Search (BFS) to find all reachable
\CodeIn{Thread.start()} calls (line 7). Each \CodeIn{Thread.start()} call
indicates that a new, non-UI thread is spawned.  After that, 
the algorithm uses a BFS to find reachable UI-accessing methods (lines 9 -- 23)
from each \CodeIn{Thread.start()} node.
Specifially, it uses a queue to keep track of all visited nodes, and
then checks every successive node to be visited (line 12);
it reports an error if that node
is a UI-accessing method (line 15), or skips it if it is
a safe method (line 17), or simply keeps traversing otherwise (line 19).

@@

To alleviate this limitation, we present an algorithm to construct
a reflection-aware call graph based on simple program transformation.
The basic idea to replace reflection calls with explicit object
creation instructions, pretending the corresponding concreate object
has been created.  The algorithm is shown in Figure~\ref{fig:cgalgorithm}.
It consists of two steps. The first step is a simple program
transformation to replace reflection calls with object creations, and
the second step is to use standard call graph construction algorithms
to construct the graph on the transformed program. Lines 1 - 7 show
the transformation step. The algorithm iterates through every statement
in an analyzed program. When it sees a reflection call statement (e.g.,
the \CodeIn{findViewById} method), the algorithm analyzes the
program to determine a set of possible classes that may be created.
After that, the algorithm creates a new instruction which non-deterministically
returns a new object of the class set. The reflection-aware call graph
construction algorithm is indepdent of the underlying call graph algorithm;
any existing algorithm can be used to construct the resulting graph at line 8.

@@

%An eclipse plugin is an open program. 
Unlike a SWT desktop application, an Eclipse plugin does not
have a main method as a single program entry point. Instead, it extends
extension points provided by the Eclispe framework to implement
functionalities. When a plugin starts, Eclipse
calls back the overrided extension points to handle the
upcoming events. We customize our technique for Eclipse plugin as follows:

@@

\item \textbf{Call graph entry nodes: } all overriden SWT
GUI event handling methods\footnote{Eclipse plugin is built
on top of the SWT framework} are called from the UI thread.
We treat these callback methods as the entry nodes.

@@

%entry nodesall overriden methods of the classes inside
% a plugin's \CodeIn{ui} package.  Such methods are normally called by the eclipse framework
%by the UI thread. XXX This rule, though quite heuristical, works quite well in practice.

@@

\item \textbf{Call graph entry nodes: } all overriden callback methods in 
Swing's UI listerner classes are called from the UI thread. We treat those callback
methods as the entry nodes.

%Specifically, for each class, we check whether
%it is a Swing listerner class. If so, we extract all its overriden callback methods as the call graph entry points.
 %Such methods are normally called by the eclipse framework
%by the UI thread. XXX This rule, though quite heuristical, works quite well in practice.

@@

\item \textbf{Call graph entry nodes: } in an Android application,
an \CodeIn{Activity} object is created and manipulated by the UI thread. We treat
all public methods from an \CodeIn{Activity} class as call graph entry nodes. Additionally,
we also add all overriden callback methods in event listener classes as entry nodes.

>>>>

Our algorithm in Figure~\ref{fig:detectalgorithm} works as follows. It
first constructs a static call graph for the tested program (line 2),
then specifies entry nodes for it (line 3). The algorithm starts to traverse
the call graph from every entry node (line 6). For every entry node,
it first uses Breadth First Search (BFS) to find all reachable
\CodeIn{Thread.start()} calls (line 7). Each \CodeIn{Thread.start()} call
indicates that a new, non-UI thread is spawned.  After that, 
the algorithm uses a BFS to find reachable UI-accessing methods (lines 9 -- 23)
from each \CodeIn{Thread.start()} node.
Specifically, it uses a queue to keep track of all visited nodes, and
then checks every successive node to be visited (line 12);
it reports an error if that node
is a UI-accessing method (line 15), or skips it if it is
a safe method (line 17), or simply keeps traversing otherwise (line 19).

@@

To alleviate this limitation, we present an algorithm to construct
a reflection-aware call graph based on simple program transformation.
The basic idea to replace reflection calls with explicit object
creation instructions, pretending the corresponding concrete object
has been created.  The algorithm is shown in Figure~\ref{fig:cgalgorithm}.
It consists of two steps. The first step is a simple program
transformation to replace reflection calls with object creations, and
the second step is to use standard call graph construction algorithms
to construct the graph on the transformed program. Lines 1 - 7 show
the transformation step. The algorithm iterates through every statement
in an analyzed program. When it sees a reflection call statement (e.g.,
the \CodeIn{findViewById} method), the algorithm analyzes the
program to determine a set of possible classes that may be created.
After that, the algorithm creates a new instruction which non-deterministically
returns a new object of the class set. The reflection-aware call graph
construction algorithm is independent of the underlying call graph algorithm;
any existing algorithm can be used to construct the resulting graph at line 8.

@@

%An eclipse plugin is an open program. 
Unlike a SWT desktop application, an Eclipse plugin does not
have a main method as a single program entry point. Instead, it extends
extension points provided by the Eclispe framework to implement
functionalities. When a plugin starts, Eclipse
calls back the overridden extension points to handle the
upcoming events. We customize our technique for Eclipse plugin as follows:

@@

\item \textbf{Call graph entry nodes: } all overridden SWT
GUI event handling methods\footnote{Eclipse plugin is built
on top of the SWT framework} are called from the UI thread.
We treat these callback methods as the entry nodes.

@@

%entry nodesall overriden methods of the classes inside
% a plugin's \CodeIn{ui} package.  Such methods are normally called by the eclipse framework
%by the UI thread. XXX This rule, though quite , works quite well in practice.

@@

\item \textbf{Call graph entry nodes: } all overridden callback methods in 
Swing's UI listener classes are called from the UI thread. We treat those callback
methods as the entry nodes.

%Specifically, for each class, we check whether
%it is a Swing listener class. If so, we extract all its overridden callback methods as the call graph entry points.
 %Such methods are normally called by the eclipse framework
%by the UI thread. XXX This rule, though quite heuristical, works quite well in practice.

@@

\item \textbf{Call graph entry nodes: } in an Android application,
an \CodeIn{Activity} object is created and manipulated by the UI thread. We treat
all public methods from an \CodeIn{Activity} class as call graph entry nodes. Additionally,
we also add all overridden callback methods in event listener classes as entry nodes.
